Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-10 trunk/lids/twittersearchwrap/paper/paper.tex

\begin{figure}[htb]
  \centering
  \includegraphics[width=.6\linewidth]{architecture}
  \caption{System Architecture}
  \label{fig:arch}
\end{figure}

@@

An example for a single retrieved post is the following: ''\texttt{Just
returned from a wonderful holiday in \#ka.
\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}'', posted by
Twitter user \texttt{sample\_user\_12345}; geo coordinates and the date
the message has been posted are furthermore known.

@@

In our example, the message contains a link to
\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the
tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the
text found at the link gives us the following text: ''\texttt{Karlsruhe, where
paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''

	\item In a third step entities matching the search result are retrieved. The content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation. The result of this step is a list of matching articles of the English Wikipedia.

In our example, the contents of all posts related to the search term '\#ka' are merged with the retrieved external website content. Thus, the post obtained from step 1 would be matched with the website content obtained in step 2 into a single input stream: \texttt{Just returned from a wonderful holiday in \#ka. \url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets. Karlsruhe, where paths \newline converge - a legendary city in the sunny south-west of Germany, famed for its \newline fan-shaped historic street plan, where margraves reigned in times past, and German \newline joie de vivre reigns today.} 
This string is appended to the Twitter content and the external content of all other posts in the result.

@@

	Continuing our example, the output RDF document contains the following triples
	to reference the DBPedia mappings:\newline
	\texttt{<rdf:Description rdf:about=""/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
	Karlsruhe\_Institute\_of\_Technology"/>}\newline
	\texttt{</rdf:Description>}\newline
	The Twitter posts matching the search term \#ka are all described in the output document. As an example, the description for the initially given post results in the following RDF output:

	\texttt{<rdf:Description rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
	show/1234567890\#id">\newline
	<foaf:page rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
	<geo:lat>49.010239</geo:lat>\newline 
	<geo:long>8.411879</geo:long>\newline
	<foaf:maker rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
	show?screen\_name=sample\_user\_12345\#id"/>\newline 
	<dc:description>\newline
	Just returned from a wonderful holiday in \#ka.
	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
	</dc:description>\newline
	</rdf:Description>\newline}
\end{enumerate}

@@

The optional step of dereferencing URLs which are posted in messages contained
in the result set can be triggered using the option \texttt{extern=true} in our system. To keep the input size for the next steps manageable, we do not use the whole content of the referenced sites but only the first 50 words.

@@

The RDF document describes the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}. The annotations are added to the search result using \texttt{rdf:seeAlso} links to DBpedia entities \cite{key:dbpedia} which are obtained by a direct transformation of the Wikipedia entities' URLs. DBpedia has been chosen as these entities allow for a more coherent presentation of the content in the context of RDF.

\myremark{Uta}{David, kannst Du das Ausgabeformat noch etwas ausführlicher beschreiben? Welche Informationen werden genau dargestellt, welche Relationen werden wofür verwendet?}

%The implemented system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
%the Twitter search term and returns a RDF}
%document semantically describing the most recent Twitter messages matching the
%given query. The returned RDF document furthermore contains a mapping of the
%query to Encyclopedia articles which based on the content published by users that most recently used the search
%term in their posts maps to articles best describing the content of Twitter
%messages related to the term. An overview of the System Architecture is given in Figure
%\ref{fig:arch}.\newline 
%Taking a more detailed look, methods performed by the
%Twitter Search Wrapper can be grouped into five sequential steps (see Figure
%\ref{fig:arch}). We will follow those steps along a simple example, using
%\#ka (a hashtag frequently used to describe posts related to the city of
%Karlsruhe, Germany) as search term for the Twitter Search wrapper.

%\begin{enumerate}
%  \item 
%In a first step the Twitter Search Wrapper fetches the atom feed (XML Data)
%generated by the Twitter Search
%API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given
%search query. The generated feed contains the data of the 100 most recently published
%publicly visible Twitter messages and their authors which match the search query.
%The messages themselves are described by their content, publishing date, authors
%and optionally a geographic location.\linebreak\linebreak
%In the given example, calling the Wrapper with query '\#ka' will return a
%document containing all most recent Twitter posts and their meta information
%whose content matched the search string '\#ka'. Taking a closer look, a single
%retrieved post might have the following content: \newline\linebreak 
%\texttt{Just returned from a wonderful holiday in \#ka.
%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}
%\linebreak
%\item
%In a second (optional) step hyperlinks posted in messages of the fetched
%feed are followed, content of the referenced website's body is fetched and
%processed to the Wrapper. This option is triggered calling the Twitter Search
%Wrapper with attribute extern=true.\newline
%\linebreak
%Following the initial example, the given sample post contained a link to
%\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe, which contains the following
%text:\newline
%\linebreak
%''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
%south-west of Germany,\newline famed for its fan-shaped historic street plan,
%where margraves reigned in times past,\newline and German joie de vivre reigns
%today.}''\newline\linebreak
%The text is fetched and returned to the Wrapper. The same accounts for
%content of all other websites that were referenced in the list of posts matching
%the query \#ka.\newline
%\item
%The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
%the Twitter messages that matched the search query and optional content of their
%referenced websites is merged to a single input string which is used as input for the Wikifier. The service
%returns a list of matching articles of the English
%Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
%to trigger mapping to the German Wikipedia.\newline\linebreak
%In the given example, content of all posts related to the search term '\#ka' is
%merged with retrieved external website content. Taking a closer look at the
%single post we merge its content and content of its referenced website to
%a single string:\newline\linebreak
%\texttt{Just returned from a wonderful holiday in \#ka.
%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets. Karlsruhe,
%where paths converge - a legendary city in the sunny\newline south-west of
%Germany, famed for its fan-shaped historic street plan, where margraves\newline
%reigned in times past, and German joie de vivre reigns today.}\newline\linebreak
%This string is appended to Twitter content and external content of all other
%posts that have been retrieved in this way matching the initial query \#ka and
%used as input for the Wikifier.\newline
%  \item
%The Wikifier now maps the input string to relevant Wikipedia articles. A
%detailed description of this process can be found under \cite{key:wikifier}. 
%The list of matching Wikipedia articles is finally returned to the
%Wrapper.\newline\linebreak
%In the given example, a desired mapping of the contents of posts related to the
%hashtag \#ka and mapping for the hashtag \#ka as such, would preferably be a
%mapping to Wikipedia articles describing content related to Karlsruhe. We just
%assume this results in mappings to the articles for Karlsruhe, Germany and the
%Karlsruhe\_Institute\_of\_Technology.\newline
%  \item
%The Wrapper finally generates a RDF document using popular ontologies
%(foaf\footnote{http://xmlns.com/foaf/spec/},
%dublincore\footnote{http://dublincore.org/documents/dcmi-terms/}, geo\footnote{http://www.w3.org/2003/01/geo}) to describe the data related to the
%returned Twitter messages and their content using 'rdfs:seeAlso' triples to link
%the document to DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted
%output of the Wikifier) that have been mapped to the documents content.
%At this point DBPedia is chosen as referenced encyclopedia, because its
%semantic nature and description of Wikipedia article content contributes to a
%coherent semantic description in the RDF document. \newline\linebreak Coming
%back to the example, the output RDF document contains the following triples to reference the
%DBPedia mappings:\newline\linebreak \texttt{<rdfs:seeAlso
%rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
%\texttt{<rdfs:seeAlso
%rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
%\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
%Karlsruhe\_Institute\_of\_Technology"/>}\newline\linebreak 
%The twitter posts matching the search term \#ka are all described in the output
%document. As an example, the description for the initially given post might
%result in the following RDF output:\newline\linebreak
%\texttt{<rdf:Description
%rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
%show/1234567890\#id">\newline <foaf:page
%rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
%<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
%<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
%<foaf:maker
%rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
%show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
%Just returned from a wonderful holiday in \#ka.
%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
%</dc:description>\newline
%</rdf:Description>\newline}
%\end{enumerate}

@@

fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & 0.0208 & 0.0204 \\

@@

news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & 0.0000 & 0.0000  \\
jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & 0.0000 & 0.0000 \\
libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & 0.0208 & 0.0204 \\
followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & 0.0000 & 0.0000\\

@@

sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & 0.0000 & 0.0000 \\

@@

nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & 0.0000 & 0.0000 \\

@@

followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	0.0000 &	0.0000 \\

@@

win & 20 & 0 & 4.2949 & 5.1856 & 0.0347 & 0.0221 & 0.0000 & 0.0000 \\
tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & 0.0000 & 0.0000 \\
music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & 0.0208 & 0.0204 \\

@@

bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & 0.0208 & 0.0204  \\

>>>>

\begin{figure}[htb]
  \centering
  \includegraphics[width=.7\linewidth]{architecture}
  \caption{System Architecture}
  \label{fig:arch}
\end{figure}

@@

An example for a single retrieved post is the following: \begin{sloppypar}
''\texttt{Just
returned from a wonderful holiday in \#ka.
\url{http://www.karlsruhe.de/stadt/tourismus.en}
@KarlsruheTweets}'',\end{sloppypar} posted by Twitter user
\texttt{sample\_user\_12345}; geo coordinates and the date the message has been posted are furthermore known.

@@

In our example, the message contains a link to
\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the
tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the
text found at the link gives us the following text:
\begin{sloppypar}''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''
\end{sloppypar}	
	\item In a third step entities matching the search result are retrieved. The
	content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation. The result of this step is a list of matching articles of the English Wikipedia.

In our example, the contents of all posts related to the search term '\#ka' are
merged with the retrieved external website content. Thus, the post obtained from
step 1 would be matched with the website content obtained in step 2 into a
single input stream: \begin{sloppypar}"\texttt{Just returned from a wonderful
holiday in \#ka. \url{http://www.karlsruhe.de/stadt/tourismus.en}
@KarlsruheTweets. Karlsruhe, where paths converge - a legendary city in the
sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}"\end{sloppypar}This string is appended to the Twitter content and the external content of all other posts in the result.

@@

	Continuing our example, the output RDF document should contain the following
	triples to reference the DBPedia mappings:
    \begin{enumerate}
      \item \texttt{\#ka rdfs:seeAlso http://dbpedia.org/resource/Karlsruhe.}
      \item \texttt{\#ka rdfs:seeAlso http://dbpedia.org/resource/Germany.}
      \item \texttt{\#ka rdfs:seeAlso\newline
      http://dbpedia.org/resource/Karlsruhe\_Institute\_of\_Technology.}
    \end{enumerate}

	The Twitter posts matching the search term \#ka are likewise all described in
	the output document. Here, the description for the initially given post
	abbreviated \texttt{m} results in the following
	triples:
	\begin{enumerate}
      \item \texttt{twitter:m foaf:page\newline
      ``http://twitter.com/sample\_user\_12345/statuses/1234567890.''}
      \item \texttt{twitter:m dc:date ``2011-02-23T12:00:00Z''.}
      \item \texttt{twitter:m geo:lat ``49.010239''.}
      \item \texttt{twitter:m geo:long ``8.411879''.}
      \item \texttt{twitter:m foaf:maker twitter:sample\_user\_12345}
      \item \texttt{twitter:m dc:description ``Just returned from a
      wonderful\newline holiday in
      \#ka.\url{http://www.karlsruhe.de/stadt/tourismus.en}\newline @KarlsruheTweets''.}
    \end{enumerate}
\end{enumerate}

@@

The optional step of dereferencing URLs which are posted in messages contained
in the result set can be triggered using the option \texttt{extern=true} in our
system. To keep the input size for the next steps manageable, we do not use the
whole content of the referenced sites but only the first 50 words. The content
retrieved from external websites is beautified for our purpose removing
HTML-tags and scripting elements using the CyberNeko Java HTML Parser
Library\footnote{\url{http://sourceforge.net/projects/nekohtml/}}.

@@

The system generates and outputs an RDF document containing a
semantic description of the retrieved messages matching the search query for the
given query and references to the DBpedia articles that have been returned by the Wikifier. It describes
the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}. The annotations are added to the search result using \texttt{rdf:seeAlso} links to DBpedia entities \cite{key:dbpedia} which are obtained by a direct transformation of the Wikipedia entities' URLs. DBpedia has been chosen as these entities allow for a more coherent presentation of the content in the context of RDF.

The example twitter message given in the previous section is represented in
the output of the Twitter Search Wrapper as follows:\newline
\linebreak
\texttt{<rdf:Description
rdf:about="http://km.aifb.kit.edu/services/\newline
twitterwrap/statuses/show/1234567890\#id">\newline
	<foaf:page
	rdf:resource="http://twitter.com/sample\_user\_12345/\newline
	statuses/1234567890"/>\newline
	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline <geo:lat>49.010239</geo:lat>\newline 
	<geo:long>8.411879</geo:long>\newline
	<foaf:maker
	rdf:resource="http://km.aifb.kit.edu/services/\newline
	twitterwrap/users/show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
	Just returned from a wonderful holiday in \#ka.
	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
	</dc:description>\newline
	</rdf:Description>\newline}
	\linebreak
Furthermore the mappings to DBpedia articles returned by the Wikifier
are represented in the output document. In the Twitter Search Wrapper the
representation is done the following way, again using the introductory
example from the previous section:\newline
\linebreak
	\texttt{<rdf:Description rdf:about=""/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
	Karlsruhe\_Institute\_of\_Technology"/>}\newline
	\texttt{</rdf:Description>}\newline

@@

fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & - & - \\

@@

news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & - & -  \\
jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & - & - \\
libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & - & - \\
followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & - & -\\

@@

sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & - & - \\

@@

nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & - & - \\

@@

followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	- &	- \\

@@

win & 20 & 0 & 4.2949 & 5.1856 & 0.0347 & 0.0221 & - & - \\
tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & - & - \\
music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & - & - \\

@@

bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & - & -  \\
